Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
remove unnecessary paragraphsentence
verifiable collection pret-a

>>>>

\term{\pv{}} publishes the information on the right-hand side of each ballot, which mirrors the information contained on the corresponding voter's receipt.
So, any voter who retains her receipt can verify that her vote was recorded exactly as cast.
Moreover, if she discovers a mismatch, her signed receipt provides proof to that effect and can thus be used to call
the election result into question.
